Trajectories: how functional traits influence plant growth and shade tolerance across the life-cycle

### 2016-10-17 ms/figure_conceptual.tex
Incorporate suggestions from R Duursma throughout article
Cannot have 'con' directory on windows

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{{\rm d}B}{{\rm d}t}$}{output/con/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{\scriptsize $\quad c$}{output/con/net_mass_production_dt_yield}{}
\othercol{3}{\hspace{-1em}$\times\Bigg($\hspace{-0.3em}\scriptsize$A_{\rm l} \bar{p}$}{output/con/net_mass_production_dt_assimilation}{}
\othercol{4}{\hspace{-1em}-$\Sigma$\scriptsize $M_{\rm i} r_{\rm i}$}{output/con/net_mass_production_dt_respiration}{\hspace{-0.5em}$\Bigg)$}
\othercol{5}{\hspace{-0.75em}-$\Sigma$\scriptsize $M_{\rm i} k_{\rm i}$}{output/con/net_mass_production_dt_turnover}{}
\rowlabel{eq:dbdt}

\defineRow{1}{thisrow}
\rowtitle{Mass growth}
\firstcol{1}{$\frac{{\rm d}M_{{\rm t}}}{{\rm d}t}$}{output/con/mass_total_dt_mass_total_dt}{}
\othercol{2}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/con/mass_total_dt_fraction_allocation_growth}{$\times$}
\othercol{3}{$\frac{{\rm d}B}{{\rm d}t}$}{output/con/mass_total_dt_net_mass_production_dt}{$+$}
\othercol{4}{$\frac{{\rm d}M_{{\rm h}}}{{\rm d}t}$}{output/con/mass_total_dt_mass_heartwood_dt}{}
\rowlabel{eq:dMtdt}

\defineRow{2}{thisrow}
\rowtitle{Leaf deployment per mass invested}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm a}}}$}{output/con/darea_leaf_dmass_live_darea_leaf_dmass_live}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}M_{{\rm l}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_leaf_darea_leaf}{+}
\othercol{3}{$\frac{{\rm d}M_{{\rm r}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_root_darea_leaf}{+}
\othercol{4}{$\frac{{\rm d}M_{{\rm b}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_bark_darea_leaf}{+}
\othercol{5}{$\frac{{\rm d}M_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_sapwood_darea_leaf}{$\Bigg)^{-1}$}
 \rowlabel{eq:daldmt}

\defineRow{3}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_leaf_dt_area_leaf_dt}{}
\othercol{2}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm a}}}$}{output/con/area_leaf_dt_darea_leaf_dmass_live}{$\times$}
\othercol{3}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/con/area_leaf_dt_fraction_allocation_growth}{$\times$}
\othercol{4}{$\frac{{\rm d}B}{{\rm d}t}$}{output/con/area_leaf_dt_net_mass_production_dt}{}
\rowlabel{eq:daldt}

\defineRow{4}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{{\rm d}H}{{\rm d}t}$}{output/con/height_dt_height_dt}{}
\othercol{2}{$\frac{{\rm d}H}{{\rm d}A_{{\rm l}}}$}{output/con/height_dt_dheight_darea_leaf}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_leaf_dt_area_leaf_dt}{}
\rowlabel{eq:dhdt}

\defineRow{5}{thisrow}
\rowtitle{Stem-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/con/area_stem_dt_area_stem_dt}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}A_{{\rm b}}}{{\rm d}A_{{\rm l}}}$}{output/con/area_stem_dt_darea_bark_darea_leaf}{$+$}
\othercol{3}{$\frac{{\rm d}A_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/con/area_stem_dt_darea_sapwood_darea_leaf}{\hspace{-0.3em}$\Bigg)$}
\othercol{4}{\hspace{-0.4em}$\times\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_stem_dt_area_leaf_dt}{$+$}
\othercol{5}{$\frac{{\rm d}A_{{\rm h}}}{{\rm d}t}$}{output/con/area_stem_dt_area_heartwood_dt}{}
\rowlabel{eq:dast}

\defineRow{6}{thisrow}
\rowtitle{Stem-diameter growth}
\firstcol{1}{$\frac{{\rm d}D}{{\rm d}t}$}{output/con/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{{\rm d}D}{{\rm d}A_{{\rm st}}}$}{output/con/diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/con/diameter_stem_dt_area_stem_dt}{}
\rowlabel{eq:dDdt}

>>>>

% Needed to set equation counter, following inclusion of figure 1
\setcounter{equation}{2}

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{\hspace{-1em} \scriptsize $\alpha_{\rm \tiny bio} \alpha_{\rm \tiny y}$}{output/conn/net_mass_production_dt_yield}{}
\othercol{3}{\hspace{-1em}$\times\Bigg($\hspace{-0.3em}\scriptsize$A_{\rm l} \bar{p}$}{output/conn/net_mass_production_dt_assimilation}{}
\othercol{4}{\hspace{-1em}-$\Sigma$\scriptsize $M_{\rm i} r_{\rm i}$}{output/conn/net_mass_production_dt_respiration}{\hspace{-0.5em}$\Bigg)$}
\othercol{5}{\hspace{-0.75em}-$\Sigma$\scriptsize $M_{\rm i} k_{\rm i}$}{output/conn/net_mass_production_dt_turnover}{}
\rowlabel{eq:dbdt_2}

\defineRow{1}{thisrow}
\rowtitle{Mass growth}
\firstcol{1}{$\frac{{\rm d}M_{{\rm t}}}{{\rm d}t}$}{output/conn/mass_total_dt_mass_total_dt}{}
\othercol{2}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/conn/mass_total_dt_fraction_allocation_growth}{$\times$}
\othercol{3}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/mass_total_dt_net_mass_production_dt}{$+$}
\othercol{4}{$\frac{{\rm d}M_{{\rm h}}}{{\rm d}t}$}{output/conn/mass_total_dt_mass_heartwood_dt}{}
\rowlabel{eq:dMtdt}

\defineRow{2}{thisrow}
\rowtitle{Leaf deployment per mass invested}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm a}}}$}{output/conn/darea_leaf_dmass_live_darea_leaf_dmass_live}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}M_{{\rm l}}}{{\rm d}A_{{\rm l}}}$}{output/conn/darea_leaf_dmass_live_dmass_leaf_darea_leaf}{+}
\othercol{3}{$\frac{{\rm d}M_{{\rm r}}}{{\rm d}A_{{\rm l}}}$}{output/conn/darea_leaf_dmass_live_dmass_root_darea_leaf}{+}
\othercol{4}{$\frac{{\rm d}M_{{\rm b}}}{{\rm d}A_{{\rm l}}}$}{output/conn/darea_leaf_dmass_live_dmass_bark_darea_leaf}{+}
\othercol{5}{$\frac{{\rm d}M_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/conn/darea_leaf_dmass_live_dmass_sapwood_darea_leaf}{$\Bigg)^{-1}$}
 \rowlabel{eq:daldmt}

\defineRow{3}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_leaf_dt_area_leaf_dt}{}
\othercol{2}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm a}}}$}{output/conn/area_leaf_dt_darea_leaf_dmass_live}{$\times$}
\othercol{3}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/conn/area_leaf_dt_fraction_allocation_growth}{$\times$}
\othercol{4}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/area_leaf_dt_net_mass_production_dt}{}
\rowlabel{eq:daldt}

\defineRow{4}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{{\rm d}H}{{\rm d}t}$}{output/conn/height_dt_height_dt}{}
\othercol{2}{$\frac{{\rm d}H}{{\rm d}A_{{\rm l}}}$}{output/conn/height_dt_dheight_darea_leaf}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_leaf_dt_area_leaf_dt}{}
\rowlabel{eq:dhdt}

\defineRow{5}{thisrow}
\rowtitle{Stem-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_stem_dt}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}A_{{\rm b}}}{{\rm d}A_{{\rm l}}}$}{output/conn/area_stem_dt_darea_bark_darea_leaf}{$+$}
\othercol{3}{$\frac{{\rm d}A_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/conn/area_stem_dt_darea_sapwood_darea_leaf}{\hspace{-0.3em}$\Bigg)$}
\othercol{4}{\hspace{-0.4em}$\times\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_leaf_dt}{$+$}
\othercol{5}{$\frac{{\rm d}A_{{\rm h}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_heartwood_dt}{}
\rowlabel{eq:dast}

\defineRow{6}{thisrow}
\rowtitle{Stem-diameter growth}
\firstcol{1}{$\frac{{\rm d}D}{{\rm d}t}$}{output/conn/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{{\rm d}D}{{\rm d}A_{{\rm st}}}$}{output/conn/diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/conn/diameter_stem_dt_area_stem_dt}{}
\rowlabel{eq:dDdt}
